
\documentclass{muratcan_cv}
%!TEX TS-program = xelatex
\setname{\textcolor{cyan}{\textbf{Veera Bhadrachary}}}{\textcolor{cyan}{\textbf{Gade}}}
\setaddress{D.no: 12-24/3,\hspace{1mm}P.W.D Colony, \hspace{1mm}Janapadu road,\hspace{1mm} Piduguralla, \hspace{1mm}Guntur,\hspace{1mm} A.P,\hspace{1mm} India\hspace{1mm}-\hspace{1mm}522413.}
\setmobile{+91 8978975688}
\setmail{gvbc042@gmail.com}
\setposition{Work Student} %ignored for now
\setlinkedinaccount{https://www.linkedin.com/in/veera-bhadrachary-734244a4/} %you can play with color of the template (red is also nice..)
\setgithubaccount{https://github.com/gvbc42/Veerabhadra} %you can play with color of the template (red is also nice..)
\setthemecolor{cyan} %you can play with color of the template (red is also nice..)

\begin{document}
%Set variables
%You can add sections, texts, explanations just by copying the style below. Replace the dummy texts "\lipsum[1][x-x]\par" with actual texts.
%Create header
\headerview
\vspace{1ex}
%Sections
%
% Summary
\addblocktext{Career overview}{An innovative and enthusiastic electrical engineer is passionate to become data scientist. Through my 5 years of teaching experience about bringing exceptional lecturing skills and expertise in modelling power system models in various academic software platforms. Moreover, through my 3.5 years of Ph.D research work about application of least square regression method for stability, security, and economy optmization in power systems by using meta-heuristic algorithms. Profiient in creating data regression models,building predictive modeles, data processing, and data visualising  in python to solve problems. Also, relevent skills include Jupiter, numpy, pandas, matplotlib, seaborn, statastics, scikit-learn, and machine learning.
}%
% Skills
\section{Skills}
%
\newcommand{\skillone}{\createskill{Programming Languages}{\textbf{\emph{Experienced:}} \ \  Python \cpshalf Matlab \cpshalf latex-TexStudio \cpshalf Matpower \cpshalf Objective-C++ \cpshalf Objective-C}}
%
\newcommand{\skilltwo}{\createskill{Acdamic Softwares}{\textbf{\emph{Experienced:}} \ \  Matlab \cpshalf EMTP-RV \cpshalf PSCAD \cpshalf PSPICE \cpshalf PSIM}}
%
\newcommand{\skillthree}{\createskill{Acdamic Softwares}{\textbf{\emph{Familiar:}} \ \  JMAG \cpshalf POWERFORGE \cpshalf POWER WORLD \cpshalf PVSYST \cpshalf PSAT \cpshalf TINA \cpshalf OPAL-RT }}
%
\newcommand{\skillfour}{\createskill{Frameworks \ \& \ Libraries}{Jupyter \cpshalf Matplotplib \cpshalf Numpy \cpshalf Pandas \cpshalf Scikit-learn \cpshalf seaborn \cpshalf Machine learning}}
%
\newcommand{\skillfive}{\createskill{Languages}{\textbf{\emph{Native:}} \ \  Telugu \ \ \textbf{\emph{Fluent:}} \ \ English \ \ \textbf{\emph{Moderate:}} \ \  Hindi }}

\newcommand{\skillsix}{\createskill{Data Science}{\textbf{\emph{Learning:}} \ \  Machine Learning with Python course is going on now.}}
%
\createskills{\skillone, \skilltwo, \skillthree, \skillfour, \skillfive, \skillsix }

\section{Hobbies and Interests}

\newcommand{\skillseven}{\createskill{Acadamic}{\textbf{\emph{:}} \ \ Learning new softwares and tools \cpshalf Pasanate to buid models to fix problems in data science}}
%
\newcommand{\skillnine}{\createskill{Personnal}{\textbf{\emph{:}} \ \ Reading books \cpshalf Listining music}}
\createskills{\skillseven, \skillnine}
%Education
\section{Education} 
    \datedexperience{(Ph.D.) in Power Systems \hspace{51.5mm} 9.0 SGPA}{Jul 2017-\textbf{Present}}
    \explanation{Vignan's Foundation For Science, Technology \& ResearchVadlamudi,Guntur,A.P,India-52213} 
    \explanationdetail{Research Scholar and Teaching Assistant} 	
     %replace this part with actual text
    \datedexperience{M.Tech. in Power Systems \hspace{50mm} 69.87\%}{Jul 2011}
    \explanation{R.V.R \& J.C College of Engineering,Chowdavaram,Guntur,A.P,India-522019.} 
	%replace this part with actual text
	\datedexperience{B.Tech. in Electrical and Electronics Engineering \hspace{8mm} 63.08\%}{May 2008}
	\explanation{VIGNAN’S Engineering College,Vadlamudi,Guntur,A.P,India-522213.} 
	%replace this part with actual text
	\datedexperience{Diploma in Electrical and Electronics Engineering \hspace{6mm} 73.93\%}{Apr 2005}
    \explanation{K.D.R GOVT POLYTECHNIC, Wanaparthy,Mahaboobnagar,A.P,India-509103.} 
    %replace this part with actual text
    \datedexperience{I.T.I in Electrician Trade \hspace{53.5mm} 80.57\%}{Jul 2001}
    \explanation{A. P. S. W. R. ITI, Macherls,Guntur,A.P,India-522426.} 
    %replace this part with actual text
    \datedexperience{S.S.C \hspace{88.5mm} 67.66\%}{Mar 1999}
    \explanation{M.P.Z.P HIGH SCHOOL,Piduguralla,Guntur,A.P,India-522413} 
%
% Experience
\section{Professional Experience}

\datedexperience{Vignan's Foundation for Science, Technology \& Research.}{Jul 2017-Present / Guntur} 
    \explanation{Research Scholar and Teaching Assistant}
        %
\datedexperience{Sri Mittapalli College of Engineering.}{Jun 2015-Apr 2017 / Guntur} 
    \explanation{Assistant Professor}          
        %
\datedexperience{Chalapathi Institute Of Engineering and Technology.}{Jun 2011-Apr 2014 / Guntur} 
    \explanation{Assistant Professor}   
 %replace this part with actual text
         %
\datedexperience{R.V.R \& J.C College of Engineering}{Jun 2008-Apr 2009 / Guntur}
    \explanation{Lecturer} 
     % Experience

\section{Academic activities and Achievements}

    \newcommand{\extraone}{Gate rank 1466 with 90.3 Percentile (2008).\\}
    \newcommand{\extrazero}{Ratified by jntu kakinada (2015).\\}       
    \newcommand{\extratwo}{Real-Time applications of Opal-Rt for power electronics, smart grid and micro grid, organized by School of Electrical engineering,VIT Chennai.(International FDP)\\}    
    \newcommand{\extrathree}{Metaheuristic algorithm for extracting maximum power from a Solar PV generation system, organized by NIT srinagar.(IEEE webinar).\\}    
    \newcommand{\extrafour}{TEQIP-III: A 5-day continuing education program on Advanced Technologies in Power Engineering in NIT Warangal, Telangana.\\}    
    \newcommand{\extrafive}{International conference on “ Innovations in Power, Energy and Intelligent control systems ” in VFSTR, Vadlamudi, A.P.\\}    
    \newcommand{\extrasix}{Smart DC micro grid solutions remote area electrification, organized by Central university of Haryana.(webinar).\\}    
    \newcommand{\extraseven}{Smart DC micro grid solutions remote area electrification, organized by Central university of Haryana.(webinar)\\}    
    \newcommand{\extraeight}{DCS and its applications to power sector, organized by Central university of Haryana.(webinar)\\}    
    \newcommand{\extranine}{Power train and Electro magnetic transients, organized by Department of Electrical and Electronics Engineering,New Horizon College of Engineering, Bangalore, in association with PWSIM Engg. Solutions Pvt Ltd.(workshop)\\}    
    \newcommand{\extraten}{Transformer dielectric fluid technology, organized by IEEE standards association and IEEE pes gujarath chapter.\\}    
    \newcommand{\extraeleven}{Workshop on “LATEX” in VFSTR, Vadlamudi, A.P.\\}    
    \newcommand{\extratwelve}{A National Conference on “Emerging Trends in Power Energy and Contro” in VFSTR, Vadlamudi, A.P.\\}
    
        \newcommand{\listofextras}{\extraone,\extrazero, \extratwo, \extrathree, \extrafour, \extrafive, \extrasix, \extraseven, \extraeight, \extranine,\extraten, \extraeleven, \extratwelve}
    %
    \createbullets{\listofextras}

\section{Academic projects}

\textbf{\hspace{10mm}My projects}
    \newcommand{\projone}{Power system osculations damping in WSCC 9 bus system by using fuzzy-pod-upfc controller.\\}
    \newcommand{\projtwo}{Fuzzy logic control of variable speed drives.\\}
    \newcommand{\projthree}{Automatic mast light.}
    
            \newcommand{\listofproj}{\projone,\projtwo,\projthree}
    %
    \createbullets{\listofproj}
\textbf{\hspace{10mm}Projects handled during career.}

 	\newcommand{\carone}{Building integrated photovoltaic system with energy storage and smart grid communication.\\}
	\newcommand{\cartwo}{Three area load frequency  control with fuzzy and conventional controllers.\\}
	\newcommand{\carthree}{Prony analysis for power system transient harmonics.\\}
	\newcommand{\carfour}{Energy scavenging from vibrations.\\}
	\newcommand{\carfive}{Power quality improvement in WSCC 9 bus system with STATCOM.\\}
	\newcommand{\carsix}{Simulation of fuzzy logic controlled grid interactive inverter.\\}
	\newcommand{\carseven}{18-pulse ac-dc converter fed vector controlled induction motor drive.}

            \newcommand{\listofcar}{\carone,\cartwo,\carthree,\carfour,\carfive,\carsix,
            \carseven}
%
	\createbullets{\listofcar}

\section{Declaration}
%Footnote
\createfootnote
\newline
I here by declare that the above written particulars are best of my Knowledge and Belief.
\newline
\newline Date:
\newline Place: Guntur.
\newline
\newline
\newline
\newline \rightline{\textbf{\emph{G.Veera Bhadra Chary}}}
\newline \rightline{Signature.\hspace{10mm}} 



             
\end{document}
